%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Devin Hadley} \\ \vspace{1pt}
    \small 760-473-0063 $|$ \href{mailto:dchadley@calpoly.edu}{\underline{dchadley@calpoly.edu}} $|$ 
    \href{https://linkedin.devinhadley.com}{\underline{linkedin.devinhadley.com}} $|$
    \href{https://github.devinhadley.com}{\underline{github.devinhadley.com}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic State University}{San Luis Obispo, CA}
      {Bachelor of Science in Software Engineering, Junior, GPA 3.7}{September 2022 -- June 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
  {Software Engineer Intern}{June 2024 -- August 2024}
  {General Atomics Aeronautical Systems}{Poway, CA}
  \resumeItemListStart
    \resumeItem{Developed automated tests and contributed to the internal testing framework for MQ-9 Reaper ground station.}
    \resumeItem{Created Python scripts for eight comprehensive test plans, covering 3,762 procedure steps to ensure complete requirement coverage.}
    \resumeItem{Enhanced the internal testing framework by implementing OCR for HUD text recognition, allowing developers to easily convert HUD timers into integers.}
    \resumeItem{Presented results to executive management, demonstrating the cost and time benefits of automated testing.}
  \resumeItemListEnd

\resumeSubheading
  {Software Engineer Contractor}{September 2022 -- December 2022}
  {Sequoia West Properties}{La Jolla, CA}
  \resumeItemListStart
    \resumeItem{Developed a Python-based solution that that used the  Zillow API to automate the parsing and enrichment of housing leads from emails, entirely reducing manual data entry.}
    \resumeItem{Deployed the solution on an Ubuntu VPS and utilized CRON to schedule and automate the execution of scripts, ensuring the processing of over 150 leads daily and maintaining up-to-date market statuses for thousands of leads.}
  \resumeItemListEnd


  

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{GreekMate} $|$ \emph{TypeScript, Python, Django/DRF, React, Docker, GitHub Actions}}{June 2024 -- Present (Ongoing)}
\resumeItemListStart
    \resumeItem{Developed and deployed a comprehensive suite of web applications for fraternity and sorority management, integrating functionalities of \textbf{RushMate} and \textbf{DuesMate}. Leveraged TypeScript and React for the frontend, with Django REST Framework for the backend API.}
    
    \resumeSubItem{\textbf{RushMate}:}
    \begin{itemize}
        \resumeItem{Facilitated the uploading, commenting, liking, and voting on over 600 potential new members, significantly enhancing the efficiency of the recruitment process.}
    \end{itemize}

    \resumeSubItem{\textbf{DuesMate}:}
    \begin{itemize}
        \resumeItem{Designed a payment management system that supports scheduled payments and automated member notifications, streamlining financial management for chapter leadership.}
    \end{itemize}
    
    \resumeItem{Established CI/CD pipelines using GitHub Actions, integrated Docker for containerization, and automated testing to maintain high code quality.}
    
    \resumeItem{Currently migrating to AWS, utilizing App Runner for deployment, S3 for static files, and RDS for scalable database management to improve platform scalability and reliability.}
\resumeItemListEnd







    \resumeProjectHeading
      {\textbf{MyTar} $|$ \emph{C, Unix, Valgrind, GDB}}{May 2023 -- June 2023}
      \resumeItemListStart
        \resumeItem{Developed a USTAR compliant file archiver in C, enabling the creation, extraction, and listing of tar archives.}
      \resumeItemListEnd

      \resumeProjectHeading
  {\textbf{FW (Find Words)} $|$ \emph{C, Unix, Valgrind, GDB}}{May 2023 -- June 2023}
  \resumeItemListStart
    \resumeItem{Developed a unit-tested C program that implements a custom hash table to efficiently find and return the top \textit{n} most frequent words from a file.}
    \resumeItem{Implemented separate chaining for collision resolution.}
  \resumeItemListEnd


    \resumeSubHeadingListEnd

%-----------ORGANIZATIONS-----------
\section{Organizations}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer}{October 2023 -- June 2024}
      {Hack4Impact Cal Poly}{San Luis Obispo, CA}
      \resumeItemListStart
        \resumeItem{Collaborated with a team to build a volunteer registration calendar for an environmental non-profit in San Luis Obispo, improving their scheduling efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Treasurer}{June 2024 -- Present}
      {Delta Chi Fraternity}{San Luis Obispo, CA}
      \resumeItemListStart
        \resumeItem{Manage a \$215,000 annual budget, overseeing expenses, and ensuring the financial stability of the fraternity.}
        \resumeItem{Elected Treasurer by a membership of over 120 individuals, demonstrating trust and leadership.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
